OCMu64: a solver for One-sided Crossing Minimization

### 2024-06-20 tex/description.tex
Minor changes again

\begin{lemma}[Strongly fixed pair]\label{lem:sfp}
    Fix $u, v$. Suppose that for each $b \in A$ we have $\sum_{a \leq b} \bar u(a) \geq \sum_{a
    \leq b} \bar v(a)$. Then, for any $w$, we have $r(w, \bar v) \leq r(w, \bar u)$.
\end{lemma}

\begin{proof}
    If $\bar u \neq \bar v$, consider the least element $a_0 \in A$ such that $\bar u(a_0) \neq
    \bar v(a_0)$. We must have $\bar u(a_0) > \bar v(a_0)$. Consider the transformation of
    $\bar u$ which ``moves'' $\delta := \bar u(a_0) - \bar v(a_0)$ of weight from $a_0$ to its
    successor $a_1 \in A$, and call this transformed function $\bar u'$. Then
    \[
        r(w, \bar u') = r(w, \bar u) - \delta w(a_0) - \delta w(a_1) \leq r(w, \bar u).
    \]
    Since $\bar v$ can be obtained from $\bar u$ by a finite sequence of such transformations,
    the inequality follows.
\end{proof}

If $u \neq v$ satisfy the conditions of \ref{lem:sfp}, we call $(u, v)$ a \emph{strongly fixed
pair}. Note that for such a pair, $r(u, v) < 0$.

\begin{lemma}
    If $(u, v)$ is a strongly fixed pair, then $u \b v$.
\end{lemma}
\begin{proof}
    Suppose towards a contradiction that $v < x_0 < \cdots < x_k < u$ is part of an optimal
    solution. Write $X = \sum_i x_i$ for the combined function. Then by assumption $r(X, u)
    \leq 0$, and therefore $r(X, v) = W_v r(X, \bar v) \leq W_v r(X, u) \leq 0$. But then $c(v,
    X, u) \leq c(X, v, u) < c(X, u, v)$, a contradiction.
\end{proof}

>>>>

\begin{definition}
    If for every $b \in A$ we have $\sum_{a \leq b} \bar u(a) \geq \sum_{a
    \leq b} \bar v(a)$, and at least one of these inequalities is strict, we call $(u, v)$ a
    \emph{strongly fixed pair}. Note that in this case $r(u, v) < 0$.
\end{definition}
\begin{lemma}[Strongly fixed pair]\label{lem:sfp} Take $u, v \in B$ a strongly fixed pair.
    Then, for any $w$ we have $r(w, \bar v) \leq r(w, \bar u)$.
\end{lemma}
\begin{proof}
    Consider the least element $a_0 \in A$ such that $\bar u(a_0) \neq
    \bar v(a_0)$. We must have $\bar u(a_0) > \bar v(a_0)$. Now consider the transformation of
    $\bar u$ which ``moves'' $\delta := \bar u(a_0) - \bar v(a_0)$ of weight from $a_0$ to its
    successor $a_1 \in A$, and call this transformed function $\bar u'$. Then
    \[
        r(w, \bar u') = r(w, \bar u) - \delta w(a_0) - \delta w(a_1) \leq r(w, \bar u).
    \]
    Since $\bar v$ can be obtained from $\bar u$ by a finite sequence of such transformations,
    the inequality follows.
\end{proof}
\begin{lemma}
    If $(u, v)$ is strongly fixed, then $u \b v$.
\end{lemma}
\begin{proof}
    Suppose towards a contradiction that $v < x_0 < \cdots < x_k < u$ is part of an optimal
    solution. Write $X = \sum_i x_i$ for the combined function. Then by assumption $r(X, u)
    \leq 0$, and therefore $r(X, v) = W_v r(X, \bar v) \leq W_v r(X, \bar u) = W_v / W_u r(X,
    u) \leq 0$. But then $c(v, X, u) \leq c(X, v, u) < c(X, u, v)$, a contradiction.
\end{proof}
